Author Guidelines for DAGM-OAGM Submission

### 2013-09-18 itm/paper.tex
fix promises in clustering.

Before we start our investigation of semantic segmentation and object class segmentation,
we look into a general purpose clustering algorithm.
%
In clustering, the goal is to divide data points into homogeneous subsets, called
clusters.
Many different formulations of the clustering problem are given in the literature.
%
In the context of this work, clustering plays an important role in many respects:
\begin{itemize}
    \item Clustering, as a purely unsupervised methods is on one end of the spectrum of algorithms we investigate.
        When using per-image or per-pixel supervision as in the later chapters, we can use clustering to calibrate our
        expecation of what semisupervised and supervised algorithms should be able to achieve.
    \item As many other computer vision algorithms, our segmentation methods
        with critically depend on bag-of-feature representations of segments or
        images. These are build using a vocabulary of visual words, that is
        usually created via clustering.
    \item When discussing latent variable models in chapter~\ref{ch:latent}, we need to initialize our
        model to overcome the inherant symmetries. Clustering methods are a
        straight forward solution to this problem.
\end{itemize}

>>>>

Before we start our investigation of semantic segmentation and object class segmentation,
we look into a general purpose clustering algorithm.
%
In clustering, the goal is to divide data points into homogeneous subsets, called
clusters.
Many different formulations of the clustering problem are given in the literature.
%
In the context of this work, clustering plays an important role in many respects:
\begin{itemize}
    \item Clustering, as a purely unsupervised methods is on one end of the
        spectrum of algorithms we investigate.  When using per-image or
        per-pixel supervision as in the later chapters, we can use clustering
        to calibrate our expecation of what semisupervised and supervised
        algorithms should be able to achieve.

    \item Clustering algorithms build the basis of most superpixel algorithms, and
        better clustering algorithms can lead to better superpixel algorithms.

    \item As many other computer vision algorithms, our segmentation methods
        depends on bag-of-feature representations of segments or images. These
        are build using a vocabulary of visual words that is usually created
        via clustering.
\end{itemize}
